Lessons learned from bugs in models of human history

### 2020-05-21 paper.tex
discussion of Martin et al.

\title{Lessons learned from bugs in models of human history}
\author[1]{Aaron P. Ragsdale}
\author[1]{Dominic Nelson}
\author[1,$\star$]{Simon Gravel}
\author[2,$\star$]{Jerome Kelleher}
\affil[1]{McGill University and Genome Qu\'{e}bec Innovation Centre,
McGill University, Montr\'{e}al, Qu\'{e}bec, Canada}
\affil[2]{Big Data Institute, Li Ka Shing Centre for Health Information and Discovery,
University of Oxford, Oxford, United Kingdom}
\affil[$\star$]{Joint senior authors, listed alphabetically}
\maketitle

@@

Difficulties in transferability remain in the intended model (Fig.~\ref{fig:prs}), although
risk prediction in each population is significantly improved (compare to Fig.~5 in~\citet{martin2017human}).
The intended simulations indicate that the accuracy of genetic risk scores is still
substantially reduced in understudied populations (Fig.~\ref{fig:prs}E-G),
supporting the main conclusion of~\citet{martin2017human}.
However, the reduction is much less pronounced than reported.
In particular, we do not observe large differences in mean risk prediction
across populations (Fig.~\ref{fig:prs}C,D), as presented in~\citet{martin2017human}.
At least for the neutral polygenic architectures considered here, genetic drift alone
does not appear to induce large directional biases in mean predicted risk across ethnicities.

>>>>

\title{Lessons learned from bugs in models of human history}
\author[1]{Aaron P. Ragsdale}
\author[1]{Dominic Nelson}
\author[1,$\star$]{Simon Gravel}
\author[2,$\star$]{Jerome Kelleher}
\affil[1]{McGill Genome Centre and Department of Human Genetics,
McGill University, Montr\'{e}al, Qu\'{e}bec, Canada}
\affil[2]{Big Data Institute, Li Ka Shing Centre for Health Information and Discovery,
University of Oxford, Oxford, United Kingdom}
\affil[$\star$]{Joint senior authors, listed alphabetically}
\maketitle

@@

Difficulties in transferability remain in the intended model (Fig.~\ref{fig:prs}), although
risk prediction in each population is significantly improved (compare to Fig.~5 in~\citet{martin2017human}).
The intended simulations indicate that the accuracy of genetic risk scores is still
substantially reduced in understudied populations (Fig.~\ref{fig:prs}E-G),
supporting one of the main conclusions of~\citet{martin2017human}.
However, the reduction is much less pronounced than reported.
In particular, we do not observe large differences in mean predicted risk 
across populations (Fig.~\ref{fig:prs}C,D), as presented in~\citet{martin2017human}.
At least for the neutral polygenic architectures considered here, genetic drift alone
does not appear to induce large directional biases in mean predicted risk.
